\setuplayout[
header=0mm,
footer=0mm,
]
\setuphead[title][
	page=no,
	after={\blank[0mm]},
	style={\tfc\bold},
]
\setuphead[subject][
	after={\blank[0mm]},
	before={\blank[2.5mm]},
	style={\tfb\bold},
]
\setuphead[subsubject][
	after={\blank[0mm]},
	before={\blank[2.5mm]},
	style={\tf\bold},
]

\setupcolors[state=start]
\setuptype[style={\switchtobodyfont[tt,0.917em]}]

\setupinteraction[
state=start,
color=black,
]
\useURL[website][https://roman.hn][][roman.hn]
\useURL[GitHub][https://github.com/romanhn][][github.com/romanhn]
\useURL[LinkedIn][https://www.linkedin.com/in/romanhn/][][linkedin.com/in/romanhn]
\useURL[email][mailto:local-part@domain.tld][][local-part@domain.tld]
\useURL[phone][tel:+XXXXXXXXXXX][][+X (XXX) XXX-XXXX]

\setuppagenumbering[location=none]
\setupwhitespace[2mm]
\setupbodyfont[modern,ss]
\setupalign[nothyphenated]

\starttext
\title[title={Roman Hauksson-Neill}]

\from[website] \ \bullet \ \ \from[GitHub] \ \bullet \ \ \from[LinkedIn]

\from[email] \ \bullet \ \ \from[phone] \ \bullet \ \ \bold{Portland, OR}

\subject[title={Education}]

\startcolumns[n=2]
\startitemize[joinedup]
	\item Class of 2025 at the University of Texas at Dallas
	\item Pursuing Bachelor's in Computer Science
	\item 3.556 GPA
	\item National Merit Scholar
	\item Collegium V Honors Student
\stopitemize
\stopcolumns

\subject[title={Technologies and Languages}]

\startcolumns[n=3]
\startitemize[joinedup]
	\item C++
	\item Python scripting
	\item Bash scripting
	\item HTML, CSS
	\item Linux
	\item \LaTeX, \ConTeXt
	\item Git, GitHub
	\item Google Sheets
	\item Spanish
\stopitemize
\stopcolumns

\subject[title={Work Experience}]

\subsubject[title={X-Force Fellowship (Software Engineering) {\tt\small 2022 Jun – 2022 Aug}}]

Full-time software engineering contractor for the Joint Special Operations Command.

\subject[title={Leadership}]

\subsubject[title={ACM Research Director {\tt\small 2022 May – Current}}]

Directing a program to help undergraduates get into computer science research. 6 teams of 5 participants create research projects throughout the semester and present their results during a presentation and poster contest.

\subsubject[title={ACM Research Lead {\tt\small 2021 Dec – 2022 Apr}}]

Lead 4 participants (\textasciitilde 13\% acceptance rate) through a project about generating targeted password guesses using GPT-3. Winning research team out of 6.

\subsubject[title={OpenUTD Officer {\tt\small 2021 Dec – Current}}]

Student organization for Linux and other free and open-source software. Organizing technology talks, hosting coding nights, and conducting outreach.

\subject[title={Achievements}]

\subsubject[title={TexSAW 2022 CTF Winner {\tt\small 2022 Apr}}]

Won Capture The Flag competition with partner at cybersecurity conference.

\subsubject[title={HackUTD VIII Winner {\tt\small 2021 Nov}}]

Learned Flutter; helped design and code front end for an app to help international students, within 24 hours. Won the Nebula API Challenge with team of 4.

\subsubject[title={ACM Research Winner {\tt\small 2021 Sep – 2021 Nov}}]

Trained text prediction model using Tensorflow to analyze language trends on Twitter, with team of 4. Won research presentation contest vs. 5 other teams.

\stoptext
